Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-22 manu-draft.qmd
updated figures done

Figure @fig-gisworkflow

@@

Figure @fig-subtchgdatalluv

@@

Figure @fig-chgdatalluv

@@

@@

@@

@@

![Spatial analysis workflow used to identify opportunity areas for habitat conservation and restoration in the Tampa Bay watershed. Workflows are divided into binning of land use/land cover categories into relevant habitat types and spatial overlay of datasets to identify the opportunity areas.](figs/gisworkflow.png){#fig-gisworkflow fig-align="center"}

@@

Figure 4: Map of opportunity assessment

Figure 5: Map of restoration potential

>>>>

@fig-gisworkflow

@@

@fig-subtchgdatalluv

@@

@fig-chgdatalluv

@@

@fig-chgdatalluv

@@

@fig-oppmap

@@

@fig-restmap

@@

![Spatial analysis workflow used to identify opportunity areas and restoration potential in the Tampa Bay watershed. Workflows are divided into binning of land use/land cover categories into relevant habitat types and spatial overlay of datasets to identify the opportunity areas.](figs/gisworkflow.png){#fig-gisworkflow fig-align="center"}

@@

![Opportunity areas for habitat conservation and reservation in the Tampa Bay watershed.  Green indicates existing conservation, blue indicates proposed conservation, and pink indicates reservations opportunities.  Each category is also grouped into native and restorable habitats.](figs/oppmap.png){#fig-oppmap fig-align="center"}

![Habitat restoration potential in the Tampa Bay watershed. Areas are identified as those where habitat restoration could target the four identified categories as coastal uplands, freshwater wetlands, native uplands, or tidal wetlands. Categories are based on the opportunity areas and soil types.](figs/restmap.png){#fig-restmap fig-align="center"}
